qcircuit 2.5.3 Tutorial

### 2017-11-19 CO681-QuantumInformationProcessing/assignments/assignment_03.tex
Nearly solved 5

\end{document}

>>>>

\section{}
\subsection{a}
The density matrix for $\alpha\ket{00} + \beta\ket{11}$ is
$$\rho = |\alpha|^2\ket{00}\bra{00} + \alpha\beta^*\ket{00}\bra{11} + \alpha^*\beta\ket{11}\bra{00} + |\beta|^2\ket{11}\bra{11}.$$
Expanding in matrix notation we have
$$\rho = \begin{bmatrix}
|\alpha|^2 &0 & 0 &\alpha\beta^* \\
0 & 0 & 0 & 0\\
0 & 0 & 0 & 0\\
\alpha\beta^* & 0 & 0 &|\beta|^2.
\end{bmatrix}$$
So using the explicit formula for $Tr_1(\rho)$ we have
$$Tr_1(\rho) = \begin{bmatrix}
|\alpha|^2 & 0 \\
0 & |\beta|^2
\end{bmatrix}.$$

\subsection{b}
The second qubit is in state $\ket{0}$ with probability $|\alpha|^2$ and state $\ket{1}$ with probability $|\beta|^2$. Hence its average density matrix is
$$ \begin{bmatrix}
|\alpha|^2 & 0 \\
0 & |\beta|^2
\end{bmatrix}.$$

\subsection{c}
Let $A_0 = \sqrt{\frac{2}{3}}\begin{bmatrix}
1 & 0 \\ 0 & 0
\end{bmatrix}$, let $A_1 = \frac{1}{4} \begin{bmatrix}
\sqrt{2/3} & -\sqrt{2} \\ -\sqrt{2} & \sqrt{6}
\end{bmatrix}$, and let $A_2 = \frac{1}{4} \begin{bmatrix}
\sqrt{2/3} & \sqrt{2} \\ \sqrt{2} & \sqrt{6}
\end{bmatrix}.$
Let $\sigma = Tr_1(\rho) = \begin{bmatrix}
|\alpha|^2 & 0 \\
0 & |\beta|^2\end{bmatrix}$ be the density matrix of the second qubit after tracing out the first. Then
$$A_0\sigma A_0^\dagger = \frac{2}{3}\begin{bmatrix}
|\alpha|^2 & 0 \\ 0 & 0
\end{bmatrix}$$
and
$$Tr(A_0\sigma A_0^\dagger) = \frac{2}{3}|\alpha|^2.$$
Further
\begin{align*}A_1\sigma A_1^\dagger &= \frac{1}{16} \begin{bmatrix}
\sqrt{2/3} & -\sqrt{2} \\ -\sqrt{2} & \sqrt{6}
\end{bmatrix}\begin{bmatrix}
\sqrt{2/3}|\alpha|^2 & -\sqrt{2}|\alpha|^2 \\ -\sqrt{2}|\beta|^2 & \sqrt{6}|\beta|^2 \\&= 
\end{bmatrix}\\&= \frac{1}{16}\begin{bmatrix}
\frac{2}{3}|\alpha|^2 + 2|\beta|^2 & -\sqrt{2}(\sqrt{2/3}|\alpha|^2 + \sqrt{6}|\beta|^2) \\
 -\sqrt{2}(\sqrt{2/3}|\alpha|^2 + \sqrt{6}|\beta|^2) & 2|\alpha|^2 + 6|\beta|^2
\end{bmatrix}\end{align*}
and
$$Tr(A_1\sigma A_1^\dagger) = \frac{1}{16}(\frac{2}{3}|\alpha|^2 + 2|\beta|^2 + 2|\alpha|^2 + 6|\beta|^2)=\frac{1}{16}\big( (\frac{2}{3} + 2)|\alpha|^2 + 8|\beta|^2 \big).$$
Finally
$$A_2 \sigma A_2^\dagger = \frac{1}{16}\begin{bmatrix}
\frac{2}{3}|\alpha|^2 + 2|\beta|^2 & \sqrt{2}(\sqrt{2/3}|\alpha|^2 + \sqrt{6}|\beta|^2) \\
 \sqrt{2}(\sqrt{2/3}|\alpha|^2 + \sqrt{6}|\beta|^2) & 2|\alpha|^2 + 6|\beta|^2
\end{bmatrix}$$
and
$$Tr(A_2 \sigma A_2^\dagger) =\frac{1}{16}\big( (\frac{2}{3} + 2)|\alpha|^2 + 8|\beta|^2 \big).$$
The measurement probability for outcome $j \in \{0,1,2\}$ is $Tr(A_j \sigma A_j^\dagger)$ and the post-measurement state is $\frac{1}{Tr(A_j \sigma A_j^\dagger)}A_j\sigma A_j^\dagger.$

The average density matrix for the second qubit is
$$\sum_{j=0}^2 A_j \sigma A_j^\dagger.$$
\end{document}
